---
title: "Big Fat Humpback Whale Catalog"
author: "by Hannah Barrow - 2026"
output: 
  html_document:
    self_contained: false
  theme: 
      dark: "#2d5e80"
      secondary: "#2d5e80"
      success: "#2d5e80"
---

<style type="text/css">
.main-container {
  max-width: 100% !important;
  margin: 0 !important;
  padding: 0 !important;
}
.container-fluid {
  max-width: 100% !important;
  padding: 0 !important;
}
.IDs-nav a {
  display: block;
  padding: 6px 10px;
  margin-bottom: 3px;
  text-decoration: none;
  color: #2d5e80;
  border-radius: 5px;
}
.IDs-nav a:hover {
  background-color: #e8f0f5;
}
.IDs-nav {
  position: fixed;
  top: 150px;
  bottom: 0;
  width: 200px;
  overflow-y: auto;
  padding-right: 8px;
}
.image-scroll {
  display: flex !important;
  flex-direction: row !important;
  flex-wrap: nowrap !important;
  gap: 15px;
  width: 100%;
  overflow-x: auto !important;
  overflow-y: hidden;
  padding: 10px;
}
.image-scroll img {
  height: 200px !important;
  width: 500px !important;
  max-width: none !important;
  object-fit: contain;
  flex: 0 0 auto !important;
}</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval=TRUE, echo=FALSE, message=FALSE)
library(bslib)
library(shiny)
library(dplyr)
library(purrr)
library(stringr)
```

```{r info, include=FALSE}
lf <- dir(c("features"), recursive = TRUE)
#lf <- lf[! lf %in% c('SDG4.png', 'SDG5.png','test_image.jpg')]

mr <- data.frame(filepath = lf)
mr$type <- lapply(strsplit(lf, '/'),'[[',1) %>% unlist # FL or dorsal
mr$names <- lapply(strsplit(lf, '/'),'[[',2) %>% unlist # FL image or dorsal ID

side <- c()
for(i in 1:length(lf)) {
  lfi <- lf[i]
  spliti <- strsplit(lfi,'/')
  #print((spliti[[1]]))
  if(length(spliti[[1]])>2){
    side[i] <- lapply(spliti,'[[',3)
  }else{
    side[i] <- NA
  }
}
mr$side <- side %>% unlist # left or right dorsal

dorsal_img <- c()
for(i in 1:length(lf)) {
  lfi <- lf[i]
  spliti <- strsplit(lfi,'/')
  #print((spliti[[1]]))
  if(length(spliti[[1]])>3){
    dorsal_img[i] <- lapply(spliti,'[[',4)
  }else{
    dorsal_img[i] <- NA
  }
}
mr$dorsal_img <- dorsal_img %>% unlist # dorsal images

mr <- mr %>% mutate(ID = paste0(substr(mr$names, 1, 7)))
mr <- mr %>% 
  arrange(ID)

catalog_key <- read.csv('catalog_key.csv', header = TRUE)
catalog_key <- catalog_key %>% 
  select(true.id, local) %>% 
  mutate(ID = true.id)
catalog_key <- catalog_key %>% 
  arrange(true.id)

mr <- mr %>%
  left_join(catalog_key, by = "ID", relationship = "many-to-many")
mr <- mr %>% mutate(ID = paste0(ID, "_", local))
mr <- mr %>% select(-local, -true.id)
mr$ID <- ifelse(endsWith(mr$ID, "_"), substr(mr$ID, 1, 7), mr$ID)
mr <- mr %>% 
  arrange(type, "FLs", "dorsals")
mr <- mr %>% 
  arrange(substr(ID, 3, 3), ID)

IDs <- unique(mr$ID)
```

```{r cards, }
# setup ------------------------------------------------------------------------
cards <- lapply(unique(mr$ID), function(id) {
  
  IDs <- mr %>%
    filter(ID == id)
  
  images <- lapply(IDs$filepath, function(path) {
    card_image(
      src = file.path("features", path),
      loading = "lazy"
    )
  })
  
  card(
    id = paste0("card_", id),
    card_header(id),
    div(
      class = "image-scroll",
      images
    )
  )
})

# display ----------------------------------------------------------------------
page_fillable(
  layout_sidebar(
    sidebar = sidebar(
      div(
        class = "IDs-nav",
        lapply(unique(mr$ID), function(id) {
          tags$a(
            href = paste0("#card_", id),
            id
          )
        })
      )
    ),
    div(
      style = "display: grid; grid-template-columns: 1fr 1fr; gap: 20px;",
      cards
    )
  )
)
```
